Use and acquisition of causal knowledge in a decision making process

### 2018-11-25 Propuesta/Presentacion/Presentacion_Corta.tex
Plan de trabajo publicaciones y gantt

	\subsection{Specific Objectives}
	\begin{frame}
	\frametitle{Specific Objectives}
	In order to reach the General Objective we must:
	\begin{enumerate}

	\end{enumerate}
	\end{frame}

@@

\section{Working and Publications Plan}
\subsection{Working Plan}
\subsection{Publications}

>>>>

	\subsection{Specific Objectives}
	\begin{frame}
	\frametitle{Specific Objectives}
	In order to reach the General Objective we must:
	\begin{enumerate}
	\item Game between agent and Nature in order to modell agent-environment interaction.
	\item Find an adequate family of probability distributions that encode causal knowledge.
	\item General belief-updating criteria in terms of causal information.
	\end{enumerate}
	\end{frame}

@@

\section{Working and Publications Plan}
\begin{frame}
Working and Publications Plan
\end{frame}
\subsection{Working Plan}
\begin{frame}
\frametitle{Working Plan}
\begin{enumerate}
\item Literature Review.
\item Studying implications of the rationality assumption for decision making under uncertainty in causal environments.
\item Formalization of a Causal Decision Problem.
\item Propose a representation of beliefs that allow causal structure to be considered.
\item Propose and evaluate an updating criteria for causal beliefs that can be updated according to new information when involved variables are known.
\item Study the problem of on-line causal discovery (fully unknown model). Convergence of proposed solution.
\end{enumerate}
\end{frame}

\subsection{Publications Plan}
\begin{frame}
\frametitle{Publications Plan}
\begin{itemize}
\item \textbf{Year 1:} Gonzalez-Soto, M., Sucar, L.E., Escalante, H.J., \textbf{Playing against Nature: causal discovery for decision making under uncertainty}. Presented at \textbf{CausalML 2018 Workshop at ICML 2018}. July 15 2018, Stockholm, Sweden. The paper can be found at \url{https://arxiv.org/abs/1807.01268}.
\item \textbf{Year 2:} Conference Paper 2 
		\begin{itemize}
		\item The implications of Causal Relations for Decision Making: a general principle for Decision under Uncertainty.
		\item Possible Forum: Beyond Curve Fitting: Causation, Counterfactuals, and Imagination-based AI. AAAI Spring Symposium, March 25-27, 2019, Stanford, CA
		\end{itemize}
\item \textbf{Year 2:} Conference Paper 3 and 4
	\begin{itemize}
	\item When a causal model is unknown but the involved variables are known, how to encode uncertainties about causal structure in a probabilistic distribution? Bayesian Nonparametric prior that explicitly represents causal structure.
	\item When variables of the environment are unknown how to encode prior beliefs and how to update them when data is not fully observed.
	\item Possible Forum: International Conference on Bayesian Nonparametrics, International Conference on Probabilistic Graphical Models.
	\end{itemize}
\item \textbf{Year 3:} Journal Paper
		\begin{itemize}
			\item Aim: Theoretical paper of results for on-line causal learning.
		\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Gantt Diagram}
\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Propuesta/presentacion/Gantt.png}
\caption{Causal graphical model for the test scenario: the target variable \textit{Lives} is causally influenced by the disease the patient has, the treatment assigned and the survival to the secondary effects of treatment.}
\label{causal_model}
\end{center}
\vskip -0.2in
\end{figure}
\end{frame}
